Appendix A: Deep Reinforcement Learning

### 2021-06-14 appendices/appendix-A-definitions.Rmd

\begin{table}[H]
\resizebox{\textwidth}{!}{\begin{tabular}{l l l l l}
\hline
Abbreviation & Algorithm Name                                                   & Model       & Policy     & Method \\
\hline
A2C          & Advantage Actor Critic  (Mnih et al. 2016)                        & Model-free  & On-policy  & Actor-critic\\
A3C          & Asynchronous A2C  (Babaeizadeh et al. 2017)                       & Model-free  & On-policy  & Actor-critic\\
TRPO         & Trust Region Policy Optimization  (Schulman, Levine,et al. 2017)  & Model-free  & On-policy  & Policy Gradient\\
PPO          & Proximal Policy Optimization  (Schulman, Wolski, et al. 2017)     & Model-free  & On-policy  & Actor-critic\\
DQN          & Deep Q Networks   (Mnih et al. 2015)                              & Model-free  & Off-policy & Value-Based\\
DDPG         & Deep Deterministic Policy Gradient   (Lillicrap et al. 2019)      & Model-free  & Off-policy & Actor-critic\\
TD3          & Twin Delayed DDPG  (Fujimoto, Hoof, and Meger 2018)               & Model-free  & Off-policy & Actor-critic\\
SAC          & Soft Actor Critic   (Haarnoja et al. 2018)                        & Model-free  & Off-policy & Actor-critic\\
IMPALA       & Importance Weighted Actor Learner (Espeholt et al. 2018)          & Model-free  & Off-policy & Actor-critic\\
\hline
\end{tabular}}
\caption{Survey of common model-free deep RL algorithms. }
\end{table}

>>>>

\begin{table}[H]
\resizebox{\textwidth}{!}{\begin{tabular}{l l l l l}
\hline
Abbreviation & Algorithm Name                                                     & Policy     & Method \\
\hline
A2C          & Advantage Actor Critic  (Mnih et al. 2016)                         & On-policy  & Actor-critic\\
A3C          & Asynchronous A2C  (Babaeizadeh et al. 2017)                        & On-policy  & Actor-critic\\
TRPO         & Trust Region Policy Optimization  (Schulman, Levine,et al. 2017)   & On-policy  & Policy Gradient\\
PPO          & Proximal Policy Optimization  (Schulman, Wolski, et al. 2017)      & On-policy  & Actor-critic\\
DQN          & Deep Q Networks   (Mnih et al. 2015)                               & Off-policy & Value-Based\\
DDPG         & Deep Deterministic Policy Gradient   (Lillicrap et al. 2019)       & Off-policy & Actor-critic\\
TD3          & Twin Delayed DDPG  (Fujimoto, Hoof, and Meger 2018)                & Off-policy & Actor-critic\\
SAC          & Soft Actor Critic   (Haarnoja et al. 2018)                         & Off-policy & Actor-critic\\
IMPALA       & Importance Weighted Actor Learner (Espeholt et al. 2018)           & Off-policy & Actor-critic\\
\hlin
\end{tabular}}
\caption{Survey of common model-free deep RL algorithms. }
\end{table}
